Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-07-11 paper.tex
Replace Fig: homogeneous equilibrium

\subsection{Infinite Homogeneous Slab:
  Testing Thermodynamic Equilibrium}
\label{ssec:test_equilibrium}
In an optically thick region the radiation field is in thermodynamic equilibrium
with the matter.
We set up a large slab of matter in two homogeneous configurations
representative of the fluid in the Massive Collapsed Star test
(Sec.~\ref{ssec:test_collapse}) at two different radii:
at 50~km
For comparision with Collapsed Star test, we use the LS180 equation of state,
in which the equilibrium
neutrino chemical potentials are
$\mu_{\nu_e}=-0.639$~MeV, and 
$\mu_{\nu_e}=5.771$~MeV respectively
($\mu_{\bar{\nu}_e}=-\mu_{\nu_e}$ and $\mu_{\nu_x}=0$).
Plot in Fig.~\ref{fig:homogeneous_isotropic}.
\todo{run test at this thermodynamic point}

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-homogeneous_equilibrium}
  \caption{Equilibrium distribution functions in a homogeneous background
    at two thermodynamic points,
    representative of the collapse profile at
    50~km ($\varrho=1.235 \times 10^{11}\,{\rm g}\,{\rm cm}^{-3}$,
    $T=4$~MeV,
    $Y_e=0.12$) and
    200~km ($\varrho=3.026\times 10^{7}\,{\rm g}\,{\rm cm}^{-3}$,
    $T=0.5$~MeV,
    $Y_e=0.5$).
    Described in Sec.~\ref{ssec:test_equilibrium}}
  \label{fig:homogeneous_isotropic}
\end{figure}

\subsection{Infinite Homogeneous Moving Slab:
  Testing Doppler Shift}
\label{ssec:test_doppler}
We reproduce the test above, but with the matter moving in
in the $+z$ direction, with the observer stationary.
Plot in Fig.~\ref{fig:avg_eps_doppler}.
\todo{describe test}

>>>>

\subsection{Infinite Homogeneous Slab:
  Testing Thermodynamic Equilibrium}
\label{ssec:test_equilibrium}
In an optically thick region the radiation field is in thermodynamic equilibrium
with the matter.
We set up a large slab of matter in two homogeneous configurations
representative of the fluid in the Massive Collapsed Star test
(Sec.~\ref{ssec:test_collapse}) at the radius 50~km.
For comparision with Collapsed Star test, we use the LS180 equation of state,
in which the equilibrium $\nu_e$ neutrino chemical potential is
$\mu_{\nu_e}=-0.575$~MeV
($\mu_{\bar{\nu}_e}=-\mu_{\nu_e}$ and $\mu_{\nu_x}=0$).
Plot in Fig.~\ref{fig:homogeneous_isotropic}.

\begin{figure}
  \includegraphics[width=\columnwidth]{figure-mfps-50km}
  \caption{Mean free paths
    representative of the collapse profile at
    50~km ($\varrho=10^{11}\,{\rm g}\,{\rm cm}^{-3}$,
    $T=3.7$~MeV, $Y_e=0.12$).
    In the fluid rest frame these are given by
    $(\chi^*_a)^{-1}$ for the absorption
    and $(\chi_s)^{-1}$ for elastic scattering interactions.
  }
  \label{fig:mfps-50km}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figure-ferr-50km}
  \caption{Relative error in integrated equilibrium distribution functions
    in a homogeneous background at the thermodynamic point
    representative of the collapse profile at
    50~km ($\varrho=10^{11}\,{\rm g}\,{\rm cm}^{-3}$,
    $T=3.7$~MeV, $Y_e=0.12$),
    as described in Sec.~\ref{ssec:test_equilibrium}.
    As can be seen in Fig.~\ref{fig:mfps-50km} these three species
    over the given energies
    probe our numerical solution over length scales from
    100~m to $10^{5}\,{\rm km}$.
    The source of this error is the discarded boundary term
    $f_{\rm bdry}\sim10^{-6}$, described in Sec.~\ref{ssec:numerical}.
  }
  \label{fig:homogeneous_isotropic}
\end{figure}

\subsection{Infinite Homogeneous Moving Slab:
  Testing Doppler Shift}
\label{ssec:test_doppler}
We reproduce the test above, but with the matter moving in
in the $+z$ direction, with the observer stationary.
Plot in Fig.~\ref{fig:avg_eps_doppler}.
\todo{redo test at same thermo point}
\todo{describe test}
